Trinity: A Language for Multi-View Architecture Description and Control

### 2017-07-28 sigplanconf-template.tex
draft of Early Design section

>>>>

	We have implemented a simple three-tier web application example of Trinity’s encoded architecture, including server and client components. The server is connected to a database, which is external component or a component only accessible by [INSERT HERE]. The client can only interact with the database through its own getInfo port, which is a client method, that corresponds to the server’s sendInfo method port. The server’s JSON connector gives it access to the database, which provides the client’s indirect channel of communication with the database.

	While the programmer provides client and server interface code, Trinity generates code for the server’s connector, whose type is specified by the programmer. In our example, JSON connector code is generated. Referring to the architecture’s attachments the Trinity parser type checks the connect expression and the types of the requires and provides ports of the client and server respectively are matched. Then the metadata associated with the JSON connector specifies the code that must be emitted for coordinating between the requires and provides ports. The code for the client’s getInfo port, the server’s sendInfo port, and serializing and deserializing to and from JSON is generated. By allotting communication-integrity sensitive code to Trinity automatic code generation, we ensure that communication integrity between the client and database is enforced.
